---
title: "Assignment 0"
author: "Adam Cook"
date: "February 13, 2018"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Assignment 0

This assignment is to finish the 14 todos in "A (very) short introduction to R" by Paul Torfs & Claudia Brauer, which can be found here https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf

The main resource I used was the document itself, as well as the turorials at https://www.tutorialspoint.com/r/

Other resources used to assemble this report and create the repository are below:
https://nicercode.github.io/guides/reports/


http://kbroman.org/knitr_knutshell/pages/Rmarkdown.html

https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf

Finally, a link to my repositary where all files are stored is here:
https://github.com/acook13seneca/Assignment-0

#Todo 1
```{r code1}
((2018 - 2016) / (2018 - 1997)) * 100
```

#Todo 2
```{r code2}
school <- 2018 - 2016
born <- 2018 - 1997
(school / born) * 100
```

#Todo 3
```{r code3}
func1 <- c(4,5,8,11)
sum(func1)
```

#Todo 4
```{r code4}
plot1 <- rnorm(100)
plot(plot1)
```

#Todo 5
```{r code5}
help.search("sqrt")
```

#Todo 6
```{r code6}
plot1 <- rnorm(100)
plot(plot1)
```

#Todo 7
```{r code7}
P <- seq(from=31,to=60, by=1)
Q <- matrix(data=seq(from=31, to=60, by=1), ncol=5)
```

#Todo 8
```{r code8}
y1 <- rnorm(100,0, 100)
y2 <- runif(100, min=0, max=100)
y3 <- runif(100, min=0, max=100)
t <- data.frame(x = c(y1), y = c(y1 + y2), z = c(y1 + y2 + y3))
plot(t)
```

#Todo 9
1 plots the first column in a coloured plot, #2 plots column 2 in a similar way with different colours, and #3 plots column 3 with 

#Todo 10
```{r code10}
d1 <- read.table(file="tst1.txt", header=TRUE)
new <- (d1 * 5)
write.table(new, file="tst2.txt", row.names=FALSE)
```

#Todo 11
```{r code11}
x1 <- runif(100, min=0, max=100)
value <- (sqrt(mean(x1)))
value <- c(sqrt(x1))
mean(value)
```

#Todo 12
```{r code12}
dates <- strptime(c("20180202", "20171225", "20180922"), format="%Y%m%d")
pres <- c(0, 4, 4)
m <- list(c(dates), c(pres))
mat <- matrix( unlist(m), nrow=length(m))
plot(mat)
```

#Todo 13
```{r code13}
vect <- seq(from=1, to=100, by=1)
for(i in vect) {
  if((i < 5) && (i > 90)){
    print(i * 5)
  } else {
    print(i * 0.1)
  }}
```

#Todo 14
```{r code14}
fun1 = function(arg1) {
  vect <- arg1
  for(i in vect) {
    if((i < 5) && (i > 90)){
      print(i * 5)
    } else {
      print(i * 0.1)
    }
  }
}
```

#Bonus Todo, without a loop!
```{r code15}
x <- seq(1, 100, by=1)
x <- ifelse(x < 5, x*5, ifelse(x>90, x*10, x*0.1))
print(x)
```